Hydra Battles and Cie

### 2020-12-11 doc/chapter-powers.tex
correction of errors in tex files and bibliography

\section{Addition chains}
An \emph{addition chain} (In short : \emph{a chain})~\cite{brauer1939, additionchainspage} is a representation of a sequence of
intermediate steps that lead to the evaluation of some $x^n$, under the 
assumption that each of these steps is a computation of  a power $x^i$, with 
$i<n$.

>>>>

\section{Addition chains}
An \emph{addition chain} (In short : \emph{a chain})~\cite{brauer1939} is a representation of a sequence of
intermediate steps that lead to the evaluation of some $x^n$, under the 
assumption that each of these steps is a computation of  a power $x^i$, with 
$i<n$.
